### 2021-04-08 ch03_esmvaltool/esmvaltool.tex
Spell- and grammer-checked chapter 3

Since its first release in 2016 \autocite{Eyring2016a}, the \ac{ESMValTool} has
been greatly extended and improved. A schematic representation of the current
structure of the \ac{ESMValTool} is illustrated in
\cref{fig:03:esmvaltool_schematic}. The first major element of this workflow is
an extensive preprocessing of the input data. For this, the Python-based
\acf{ESMValCore} provide a set of operators (\emph{preprocessors}) that are
applied to the input data. There are two classes of preprocessors: non-optional
and optional ones. Examples for non-optional preprocessors are the input/output
operations \emph{load} (loading input data from climate models and
observations) and \emph{save} (saving the preprocessed data), which utilize the
\ac{NetCDF} format (a self-describing, machine-independent binary file format
used for the storage of array-based scientific data). Further non-optional
preprocessors include \emph{checks} and \emph{fixes} of the input data, which
test whether the input data adheres to standards given by the \ac{CMOR} format
and fixes the data if necessary. The \ac{CMOR} format ensures that the output
from the many different modeling institutes within a generation of \ac{CMIP}
follows common standards. The optional preprocessors include commonly used
operations on spatiotemporal datasets, like spatial and temporal
\emph{subsetting}, the calculation of \emph{spatial and temporal statistics},
horizontal and vertical \emph{interpolation}, land/sea/ice \emph{masking},
\emph{unit conversion}, and the calculation of \emph{multi-model statistics}. A
further example is the \emph{variable derivation}, which can be used to derive
non-\ac{CMOR} variables from the input data. The aim of the preprocessor is to
facilitate the routine evaluation of climate models by providing a set of
commonly used data operations. To reduce computation times, \ac{ESMValCore}
allows parallel preprocessing of different datasets. However, since this leads
to a higher memory usage, a compromise has to be found in practice to optimize
the use of time and memory resources.

@@

As of \TheMonth{}, 40408 lines of code have been added and 21050 lines of code
have been removed from to the GitHub repository of \ac{ESMValCore} by the
author of this thesis. Apart from general improvements of the code base, these
changes and additions mainly include new preprocessor functions that can be
applied to the input data and derivation scripts for new non-\ac{CMOR}
variables. \Cref{tab:03:changes_to_esmvalcore} shows a summary of these main
contributions, which are partly published in the scientific documentation of
\ac{ESMValCore} \autocite{Righi2020}.

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L >{\em}L L}
    \toprule
    Type & \ignorecolumntype{l}{Name} & Description \\
    \midrule
    Preprocessor & amplitude & Amplitude of periodic phenomena (\eg{} cycles)
    \\
    \cmidrule(l){2-3}
    & land/sea fraction weighting & Weighting of fields based on the land or
    sea fraction of the respective grid cells \\
    \cmidrule(l){2-3}
    & trend & Linear trend (slope of linear regression) \\
    \midrule
    Derived variable & asr & Absorbed shortwave radiation \\
    \cmidrule(l){2-3}
    & co2s & Atmospheric \acs{CO2} concentration at surface \\
    \cmidrule(l){2-3}
    & et & Evapotranspiration \\
    \cmidrule(l){2-3}
    & rlntcs & Clear-sky net \acf{TOA} longwave radiation \\
    \cmidrule(l){2-3}
    & rsntcs & Clear-sky net \acs{TOA} shortwave radiation \\
    \cmidrule(l){2-3}
    & uajet & Position of austral jet stream \\
    \bottomrule
  \end{tabulary}
  \caption[
    Summary of new preprocessor functions and variable derivation scripts
    contributed to the \acf{ESMValCore} by the author of this thesis.
  ]{
    Summary of new preprocessor functions and variable derivation scripts
    contributed to the \acf{ESMValCore} by the author of this thesis.
  }
  \label{tab:03:changes_to_esmvalcore}
\end{table}

In total, three new preprocessor functions have been added: \emph{amplitude},
\emph{land/sea fraction weighting}, and \emph{trend}. The \emph{amplitude}
preprocessor calculates the peak-to-peak amplitude of periodic phenomena along
an arbitrary coordinate, which is usually time. A common application of this
preprocessor is the computation of a variable's diurnal or seasonal cycle
amplitude, which is for example necessary for the calculation of the predictor
variable (\ac{CO2} seasonal cycle amplitude) of the emergent constraint on
\ac{CO2} fertilization by \textcite{Wenzel2016} that is also used in
\cref{ch:06:paper_gpp} to constrain the global mean \ac{GPP} at the end of the
\nth{21} century. The \emph{land/sea fraction weighting} preprocessor weights
fields with the land or sea fraction of the respective grid cells. For example,
this is necessary for the spatial integration of flux-related variables which
are reported in units of \enquote{per square meter of land/sea} and not in
\enquote{per square meter of grid cell}. After the weighting, the grid cell
areas can be used to integrate the flux-related variable over a desired region.
In this thesis, \emph{land/sea fraction weighting} is applied to \ac{GPP}
fields given by observational products and models to compute the corresponding
global mean results (see \cref{ch:06:paper_gpp}). The \emph{trend} preprocessor
calculates the linear trend of a variable along an arbitrary coordinate. The
linear trend is defined as the slope of an ordinary least squares linear
regression of the variable against the selected coordinate. For example, this
can be used to calculate the historical trend of the \ac{GSAT}, which is used
as a predictor for \ac{ECS} in several recently published emergent constraints
\autocite{JimenezdelaCuesta2019, Nijsse2020, Tokarska2020}.

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \raisebox{2.5mm}{\includegraphics[width=\columnwidth]{
      ch03_esmvaltool/figs/co2s_map.pdf}}
    \caption{}
    \label{fig:03:co2s:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch03_esmvaltool/figs/co2s_mlo_cycle.pdf}
    \caption{}
    \label{fig:03:co2s:b}
  \end{subfigure}
  \caption[
    Illustration of the atmospheric \acs{CO2} concentration at surface
    (\emph{co2}) for \acs{CMIP}6 models.
  ]{
    (a) \acs{CMIP}6 \acf{MMM} of the atmospheric \acs{CO2} concentration at
    surface (\emph{co2s}) averaged over the months \acf{JJA} of the year 2014
    in the emission-driven historical simulation. The \acs{CMIP}6 \acs{MMM}
    includes the four climate models that provide all data needed for the
    calculation of \emph{co2s} (see legend in (b)). (b) Monthly mean
    \emph{co2s} at Mauna Loa, Hawaii ($19.5 \unit{\degree N}$, $155.6
    \unit{\degree W}$) from 1958 to 2014. The black line shows observations
    from the Mauna Loa Observatory \autocite{Keeling2005}; the remaining lines
    show emission-driven historical simulations from individual \acs{CMIP}6
    models.
  }
  \label{fig:03:co2s}
\end{figure}

In addition to new preprocessor functions, six derivation scripts for the
non-\ac{CMOR} variables \emph{asr}, \emph{co2s}, \emph{et}, \emph{rlntcs},
\emph{rsntcs}, and \emph{uajet} have been implemented into the \ac{ESMValCore}.
Apart from the atmospheric \ac{CO2} concentration at surface (\emph{co2s}),
which is used in \cref{ch:06:paper_gpp} to derive the predictor variable of the
emergent constraint by \textcite{Wenzel2016}, these variables are not directly
used in this thesis but have been added to reproduce the \ac{MDER} analysis of
\textcite{Wenzel2016a} (\emph{asr} and \emph{uajet}) or have been used in
earlier versions of the studies presented in this thesis (\emph{et} for the
study presented in \cref{ch:06:paper_gpp}; \emph{rlntcs} and \emph{rsntcs} for
the studies presented in \cref{ch:04:papers_ecs_tcr_assessment}).

The absorbed shortwave radiation (\emph{asr}) is defined as the difference in
the incoming \ac{TOA} shortwave radiation and the outgoing \ac{TOA} shortwave
radiation. The atmospheric \ac{CO2} concentration at surface (\emph{co2s}) can
be calculated from the pressure level--dependent atmospheric \ac{CO2}
concentration and the surface air pressure using interpolation. An example
illustrating \emph{co2s} is given in \cref{fig:03:co2s}. \Cref{fig:03:co2s:a}
shows the \acs{CMIP}6 \ac{MMM} of the global \emph{co2s} for the months
\acf{JJA} of the year 2014 in the emission-driven historical simulation. As
expected, the map shows high atmospheric \ac{CO2} concentrations over large
metropolitan areas with high \ac{CO2} emissions (\eg{} over North America, the
Arabian Peninsula, and East Asia). Moreover, regions with high photosynthetic
activity (\eg{} the boreal forests in the Northern Hemisphere summer and the
tropical rainforests in South America) exhibit smaller \ac{CO2} concentrations.
\Cref{fig:03:co2s:b} shows the monthly mean \emph{co2s} at Mauna Loa, Hawaii
from 1958 to 2014 for observations performed at the Mauna Loa Observatory
\autocite{Keeling2005} (thick black line) and emission-driven historical
simulations from four \acs{CMIP}6 models (remaining colored lines). Apart from
the model CNRM-ESM2-1, the simulated atmospheric \ac{CO2} concentrations show
the expected seasonal cycle present in the Keeling Curve (see
\cref{fig:02:keeling_curve}). All \acp{ESM} correctly simulate the increase in
\emph{co2s} over the years. However, there are some differences in the absolute
values with the model BCC-CSM2-MR showing the largest deviations.

@@

In addition to the ported recipes, several new recipes and diagnostic scripts
have been contributed to the public \ac{ESMValTool} repository (see
\cref{tab:03:changes_to_esmvaltool} for a summary). Some of these include the
analyses performed in other \namecrefs{ch:04:papers_ecs_tcr_assessment} of this
thesis, namely \emph{recipe\_bock20jgr.yml}
(\cref{ch:04:papers_ecs_tcr_assessment}), \emph{recipe\_meehl20sciadv.yml}
(\cref{ch:04:papers_ecs_tcr_assessment}), \emph{recipe\_schlund20esd.yml}
(\cref{ch:05:paper_ecs}), and \emph{recipe\_schlund20jgr\_*.yml}
(\cref{ch:06:paper_gpp}). \emph{recipe\_ecs.yml} and \emph{recipe\_tcr.yml}
contain diagnostic scripts that allow the calculation of the climate metrics
\ac{ECS} and \ac{TCR} for arbitrary model output (see
\cref{sec:02:climate_sensitivity}), which is also used in
\cref{ch:04:papers_ecs_tcr_assessment,ch:05:paper_ecs}. Corresponding plots are
shown in \cref{fig:02:gregory_regression,fig:02:tcr}.
\emph{recipe\_cox18nature.yml} reproduces the analysis of \textcite{Cox2018},
who introduce an emergent constraint in \ac{ECS} based on a global temperature
variability metric $\Psi$. \Cref{fig:03:cox18:a} shows $\Psi$ over the past 85
years for \acs{CMIP}5 models and observations form HadCRUT4
\autocite{Morice2012}. Since high-sensitivity climate models exhibit higher
values of $\Psi$ than low-sensitivity models, an emergent relationship between
\ac{ECS} and $\Psi$ can be established (\cref{fig:03:cox18:b}). With
observations of $\Psi$, \ac{ECS} can eventually be constrained to $\left( 2.8
\pm 0.6 \right) \unit{K}$ ($66 \unit{\%}$ confidence range). The emergent
constraint by \textcite{Cox2018} is, together with ten other emergent
constraint on \ac{ECS}, analyzed in great detail for the \acs{CMIP}5 and
\acs{CMIP}6 ensemble in \cref{ch:05:paper_ecs}, which also includes a
description of the calculation of $\Psi$ in \cref{subsec:05:cox}.

An important class of recipes in the \ac{ESMValTool} covers international
climate assessments. One such example is \emph{recipe\_flato13ipcc.yml}, which
reproduces large parts of the climate model evaluation performed in chapter 9
of the \ac{IPCC}'s Fifth \acl{AR} (\acs{AR}5) \autocite{Flato2013}. For this
recipe, the two-panel figure 9.42 has been added, which shows the relationship
between the historical and pre-industrial \ac{GSAT} and \ac{ECS}
(\cref{fig:03:flato13:a}) and the relationship between \ac{TCR} and \ac{ECS}
(\cref{fig:03:flato13:b}) within the \acs{CMIP}5 ensemble.
\Cref{fig:03:flato13:a} illustrates that there is no clear connection between
\ac{ECS} and the historical or pre-industrial \ac{GSAT}, \ie{} models with high
temperatures in the historical or pre-industrial period do not necessarily
exhibit a high equilibrium warming in the future or vice versa. On the other
hand, \ac{TCR} and \ac{ECS} are in fact well correlated within the \acs{CMIP}5
ensemble as theoretically expected from \cref{eq:02:tcr_vs_ecs}. However, this
figure only shows a linear regression fit between the two variables and not the
expected reciprocal relation. The output of \emph{recipe\_flato13ipcc.yml}
provided useful input for the analysis of climate sensitivity in \acs{CMIP}6
performed in \textcite{Meehl2020}, which is also presented in
\cref{ch:04:papers_ecs_tcr_assessment}.

@@

The implemented \acs{CMOR}ization scripts (also referred to as
\emph{\acs{CMOR}izers}) allow the processing of arbitrary observational data
with the \ac{ESMValTool}. For this, the raw observational datasets are
reformatted in such way that they adhere to the \ac{CMOR} standards. Since the
\acs{CMOR}ization scripts are publicly available like any other code in the
\ac{ESMValTool} and \ac{ESMValCore} repositories, the entire scientific
community can use them to \acs{CMOR}ize the observational data. A complete list
of all eleven newly implemented \acs{CMOR}izers including the main reference
for the corresponding observational datasets is shown in
\cref{tab:03:changes_to_esmvaltool}. The majority of these datasets are used
for analysis presented in this thesis (\eg{} see
\cref{tab:05:overview_emergent_constraints,tab:06:predictors}).

>>>>

Since its first release in 2016 \autocite{Eyring2016a}, the \ac{ESMValTool} has
been greatly extended and improved. A schematic representation of the current
structure of the \ac{ESMValTool} is illustrated in
\cref{fig:03:esmvaltool_schematic}. The first major element of this workflow is
an extensive preprocessing of the input data. For this, the Python-based
\acf{ESMValCore} provide a set of operators (\emph{preprocessors}) that are
applied to the input data. There are two classes of preprocessors: non-optional
and optional preprocessors. Examples for non-optional preprocessors are the
input/output operations \emph{load} (loading input data from climate models and
observations) and \emph{save} (saving the preprocessed data), which utilize the
\ac{NetCDF} format (a self-describing, machine-independent binary file format
used for the storage of array-based scientific data). Further non-optional
preprocessors include \emph{checks} and \emph{fixes} of the input data, which
test whether the input data adheres to standards given by the \ac{CMOR} format
and fixes the data if necessary. The \ac{CMOR} format ensures that the output
from the many different modeling institutes within a generation of \ac{CMIP}
follows common standards. The optional preprocessors include commonly used
operations on spatiotemporal datasets, like spatial and temporal
\emph{subsetting}, the calculation of \emph{spatial and temporal statistics},
horizontal and vertical \emph{interpolation}, land/sea/ice \emph{masking},
\emph{unit conversion}, and the calculation of \emph{multi-model statistics}. A
further example is \emph{variable derivation}, which can be used to derive
non-\ac{CMOR} variables from the input data. The preprocessing functions of
\ac{ESMValCore} aim to facilitate the routine evaluation of climate models by
providing a set of commonly used data operations. To reduce computation times,
\ac{ESMValCore} allows parallel preprocessing of different datasets. However,
since this leads to higher memory usage, a compromise has to be found in
practice to optimize the use of time and memory resources.

@@

As of \TheMonth{}, 40408 lines of code have been added and 21050 lines of code
have been removed from the GitHub repository of \ac{ESMValCore} by the author
of this thesis. Apart from general improvements of the code base, these changes
and additions mainly include new preprocessor functions that can be applied to
the input data and derivation scripts for new non-\ac{CMOR} variables.
\Cref{tab:03:changes_to_esmvalcore} shows a summary of these main
contributions, which are partly published in the scientific documentation of
\ac{ESMValCore} \autocite{Righi2020}.

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L >{\em}L L}
    \toprule
    Type & \ignorecolumntype{l}{Name} & Description \\
    \midrule
    Preprocessor & amplitude & Amplitude of periodic phenomena (\eg{} cycles)
    \\
    \cmidrule(l){2-3}
    & land/sea fraction weighting & Weighting of fields based on the land or
    sea fraction of the respective grid cells \\
    \cmidrule(l){2-3}
    & trend & Linear trend (slope of linear regression) \\
    \midrule
    Derived variable & asr & Absorbed shortwave radiation \\
    \cmidrule(l){2-3}
    & co2s & Atmospheric \acs{CO2} concentration at the surface \\
    \cmidrule(l){2-3}
    & et & Evapotranspiration \\
    \cmidrule(l){2-3}
    & rlntcs & Clear-sky net \acf{TOA} longwave radiation \\
    \cmidrule(l){2-3}
    & rsntcs & Clear-sky net \acs{TOA} shortwave radiation \\
    \cmidrule(l){2-3}
    & uajet & Position of austral jet stream \\
    \bottomrule
  \end{tabulary}
  \caption[
    Summary of new preprocessor functions and variable derivation scripts
    contributed to the \acf{ESMValCore} by the author of this thesis.
  ]{
    Summary of new preprocessor functions and variable derivation scripts
    contributed to the \acf{ESMValCore} by the author of this thesis.
  }
  \label{tab:03:changes_to_esmvalcore}
\end{table}

In total, three new preprocessor functions have been added: \emph{amplitude},
\emph{land/sea fraction weighting}, and \emph{trend}. The \emph{amplitude}
preprocessor calculates the peak-to-peak amplitude of periodic phenomena along
an arbitrary coordinate, which is usually time. A common application of this
preprocessor is the computation of a variable's diurnal or seasonal cycle
amplitude, which is for example necessary for the calculation of the predictor
variable (\ac{CO2} seasonal cycle amplitude) of the emergent constraint on
\ac{CO2} fertilization by \textcite{Wenzel2016} that is also used in
\cref{ch:06:paper_gpp} to constrain the global mean \ac{GPP} at the end of the
\nth{21} century. The \emph{land/sea fraction weighting} preprocessor weights
fields with the land or sea fraction of the respective grid cells. For example,
this is necessary for the spatial integration of flux-related variables which
are reported in units of \enquote{per square meter of land/sea} and not in
\enquote{per square meter of grid cell}. After the weighting, the grid cell
areas can be used to integrate the flux-related variable over any desired
region. In this thesis, \emph{land/sea fraction weighting} is applied to
\ac{GPP} fields given by observational products and models to compute the
corresponding global mean results (see \cref{ch:06:paper_gpp}). The
\emph{trend} preprocessor calculates the linear trend of a variable along an
arbitrary coordinate. The linear trend is defined as the slope of an ordinary
least squares linear regression of the variable against the selected
coordinate. For example, this can be used to calculate the historical trend of
the \ac{GSAT}, which is used as a predictor for \ac{ECS} in several recently
published emergent constraints \autocite{JimenezdelaCuesta2019, Nijsse2020,
  Tokarska2020}.

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \raisebox{2.5mm}{\includegraphics[width=\columnwidth]{
      ch03_esmvaltool/figs/co2s_map.pdf}}
    \caption{}
    \label{fig:03:co2s:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch03_esmvaltool/figs/co2s_mlo_cycle.pdf}
    \caption{}
    \label{fig:03:co2s:b}
  \end{subfigure}
  \caption[
    Illustration of the atmospheric \acs{CO2} concentration at the surface
    (\emph{co2}) for \acs{CMIP}6 models.
  ]{
    (a) \acs{CMIP}6 \acf{MMM} of the atmospheric \acs{CO2} concentration at the
    surface (\emph{co2s}) averaged over the months \acf{JJA} of the year 2014
    in the emission-driven historical simulation. The \acs{CMIP}6 \acs{MMM}
    includes the four climate models that provide all data needed for the
    calculation of \emph{co2s} (see legend in (b)). (b) Monthly mean
    \emph{co2s} at Mauna Loa, Hawaii ($19.5 \unit{\degree N}$, $155.6
    \unit{\degree W}$) from 1958 to 2014. The black line shows observations
    from the Mauna Loa Observatory \autocite{Keeling2005}; the remaining lines
    show emission-driven historical simulations from individual \acs{CMIP}6
    models.
  }
  \label{fig:03:co2s}
\end{figure}

In addition to new preprocessor functions, six derivation scripts for the
non-\ac{CMOR} variables \emph{asr}, \emph{co2s}, \emph{et}, \emph{rlntcs},
\emph{rsntcs}, and \emph{uajet} have been implemented into the \ac{ESMValCore}.
Apart from the atmospheric \ac{CO2} concentration at the surface (\emph{co2s}),
which is used in \cref{ch:06:paper_gpp} to derive the predictor variable of the
emergent constraint by \textcite{Wenzel2016}, these variables are not directly
used in this thesis but have been added to reproduce the \ac{MDER} analysis of
\textcite{Wenzel2016a} (\emph{asr} and \emph{uajet}) or have been used in
earlier versions of the studies presented in this thesis (\emph{et} for the
study presented in \cref{ch:06:paper_gpp}; \emph{rlntcs} and \emph{rsntcs} for
the studies presented in \cref{ch:04:papers_ecs_tcr_assessment}).

The absorbed shortwave radiation (\emph{asr}) is defined as the difference
between the incoming \ac{TOA} shortwave radiation and the outgoing \ac{TOA}
shortwave radiation. The atmospheric \ac{CO2} concentration at the surface
(\emph{co2s}) can be calculated from the pressure level--dependent atmospheric
\ac{CO2} concentration and the surface air pressure using interpolation. An
example illustrating \emph{co2s} is given in \cref{fig:03:co2s}.
\Cref{fig:03:co2s:a} shows the \acs{CMIP}6 \ac{MMM} of the global \emph{co2s}
for the months \acf{JJA} of the year 2014 in the emission-driven historical
simulation. As expected, the map shows high atmospheric \ac{CO2} concentrations
over large metropolitan areas with high \ac{CO2} emissions (\eg{} over North
America, the Arabian Peninsula, and East Asia). Moreover, regions with high
photosynthetic activity (\eg{} the boreal forests in the Northern Hemisphere
summer and the tropical rainforests in South America) exhibit smaller \ac{CO2}
concentrations. \Cref{fig:03:co2s:b} shows the monthly mean \emph{co2s} at
Mauna Loa, Hawaii from 1958 to 2014 for observations performed at the Mauna Loa
Observatory \autocite{Keeling2005} (thick black line) and emission-driven
historical simulations from four \acs{CMIP}6 models (remaining colored lines).
Apart from the model CNRM-ESM2-1, the simulated atmospheric \ac{CO2}
concentrations show the expected seasonal cycle present in the Keeling Curve
(see \cref{fig:02:keeling_curve}). All \acp{ESM} correctly simulate the
increase in \emph{co2s} over the years. However, there are some differences in
the absolute values with the model BCC-CSM2-MR showing the largest deviations.

@@

In addition to the ported recipes, several new recipes and diagnostic scripts
have been contributed to the public \ac{ESMValTool} repository (see
\cref{tab:03:changes_to_esmvaltool} for a summary). Some of these include the
analyses performed in other \namecrefs{ch:04:papers_ecs_tcr_assessment} of this
thesis, namely \emph{recipe\_bock20jgr.yml}
(\cref{ch:04:papers_ecs_tcr_assessment}), \emph{recipe\_meehl20sciadv.yml}
(\cref{ch:04:papers_ecs_tcr_assessment}), \emph{recipe\_schlund20esd.yml}
(\cref{ch:05:paper_ecs}), and \emph{recipe\_schlund20jgr\_*.yml}
(\cref{ch:06:paper_gpp}). \emph{recipe\_ecs.yml} and \emph{recipe\_tcr.yml}
contain diagnostic scripts that allow the calculation of the climate metrics
\ac{ECS} and \ac{TCR} for arbitrary model output (see
\cref{sec:02:climate_sensitivity}), which is also used in
\cref{ch:04:papers_ecs_tcr_assessment,ch:05:paper_ecs}. Corresponding plots are
shown in \cref{fig:02:gregory_regression,fig:02:tcr}.
\emph{recipe\_cox18nature.yml} reproduces the analysis of \textcite{Cox2018},
who introduce an emergent constraint in \ac{ECS} based on a global temperature
variability metric $\Psi$. \Cref{fig:03:cox18:a} shows $\Psi$ over the past 85
years for \acs{CMIP}5 models and observations from HadCRUT4
\autocite{Morice2012}. Since high-sensitivity climate models exhibit higher
values of $\Psi$ than low-sensitivity models, an emergent relationship between
\ac{ECS} and $\Psi$ can be established (\cref{fig:03:cox18:b}). With
observations of $\Psi$, \ac{ECS} can eventually be constrained to $\left( 2.8
\pm 0.6 \right) \unit{K}$ ($66 \unit{\%}$ confidence range). The emergent
constraint by \textcite{Cox2018} is, together with ten other emergent
constraints on \ac{ECS}, analyzed in great detail for the \acs{CMIP}5 and
\acs{CMIP}6 ensemble in \cref{ch:05:paper_ecs}, which also includes a
description of the calculation of $\Psi$ in \cref{subsec:05:cox}.

An important class of recipes in the \ac{ESMValTool} covers international
climate assessments. One such example is \emph{recipe\_flato13ipcc.yml}, which
reproduces large parts of the climate model evaluation performed in chapter 9
of the \ac{IPCC}'s Fifth \acl{AR} (\acs{AR}5) \autocite{Flato2013}. For this
recipe, the two-panel figure 9.42 has been added, which shows the relationship
between the historical and pre-industrial \ac{GSAT} and \ac{ECS}
(\cref{fig:03:flato13:a}) and the relationship between \ac{TCR} and \ac{ECS}
(\cref{fig:03:flato13:b}) within the \acs{CMIP}5 ensemble.
\Cref{fig:03:flato13:a} illustrates that there is no clear connection between
\ac{ECS} and the historical or pre-industrial \ac{GSAT}, \ie{} models with high
temperatures in the historical or pre-industrial period do not necessarily
exhibit a high equilibrium warming in the future or vice versa. On the other
hand, \ac{TCR} and \ac{ECS} are well correlated within the \acs{CMIP}5 ensemble
as theoretically expected from \cref{eq:02:tcr_vs_ecs}. However, this figure
only shows a linear regression fit between the two variables and not the
expected reciprocal relation. The output of \emph{recipe\_flato13ipcc.yml}
provided useful input for the analysis of climate sensitivity in \acs{CMIP}6
performed in \textcite{Meehl2020}, which is also presented in
\cref{ch:04:papers_ecs_tcr_assessment}.

@@

The implemented \acs{CMOR}ization scripts (also referred to as
\emph{\acs{CMOR}izers}) allow the processing of arbitrary observational data
with the \ac{ESMValTool}. For this, the raw observational datasets are
reformatted in such a way that they adhere to the \ac{CMOR} standards. Since
the \acs{CMOR}ization scripts are publicly available like any other code in the
\ac{ESMValTool} and \ac{ESMValCore} repositories, the entire scientific
community can use them to \acs{CMOR}ize the observational data. A complete list
of all eleven newly implemented \acs{CMOR}izers including the main reference
for the corresponding observational datasets is shown in
\cref{tab:03:changes_to_esmvaltool}. The majority of these datasets are used
for analyses presented in this thesis (\eg{} see
\cref{tab:05:overview_emergent_constraints,tab:06:predictors}).
